---
title: "Journal (reproducible report)"
author: "Inma Mundokkil Nishth Kumar"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---
# SALES ANALYSIS-Intro to the tidyverse

Last compiled: `r Sys.Date()`
The solution code is given below:
### Step 1: Load libraries ----
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(ggplot2)
```

### Step 2: Importing Files ----
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
bikes_tbl <- read_excel(path ="C:/datascience/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("C:/datascience/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("C:/datascience/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
```

### Step 3: Examining Data ----
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
orderlines_tbl
glimpse(orderlines_tbl)
```


### Step 4: Joining Data ----
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))
bike_orderlines_joined_tbl <- orderlines_tbl %>%
left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
bike_orderlines_joined_tbl %>% glimpse()
```

### Step 5: Wrangling Data ----
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
separate(col    = location,
           into   = c("City","State"),
           sep    = ",") %>%
  
mutate(total.price = price * quantity) %>%
select(-...1, -gender) %>%
select(-ends_with(".id")) %>%
bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
select(order.id, contains("order"), contains("model"), contains("State"),
         price, quantity, total.price,
         everything()) %>%
rename(bikeshop = name) %>%
set_names(names(.) %>% str_replace_all("\\.", "_"))
```

### Step 6: Business Insights ----
#### 6.1 Sales by Location ----
##### Step 1 - Manipulate
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
sales_by_location_tbl <- bike_orderlines_wrangled_tbl %>%
  select(State, total_price) %>%
  group_by(State) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
sales_by_location_tbl
```
##### Step 2 - Visualize
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
sales_by_location_tbl
  ggplot(sales_by_location_tbl,aes(x = State, y = sales))+ 
  geom_col(fill = "#2DC6D6")+  # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by location",
    subtitle = "Upward Trend",
    x = "State", # Override defaults for x and y
    y = "Revenue"
  )
```

#### 6.2 Sales by Year and Category 2 ----
##### Step 1 - Manipulate
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
  sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
   select(order_date, total_price, State) %>%
   mutate(year = year(order_date)) %>%
   group_by(year, State) %>%
   summarise(sales = sum(total_price)) %>%
   ungroup() %>%
   mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                       decimal.mark = ",", 
                                       prefix = "", 
                                       suffix = " €"))
  sales_by_year_state_tbl
```

##### Step 2 - Visualize
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
    sales_by_year_state_tbl %>%
    ggplot(sales_by_year_state_tbl,mapping=aes(year,sales, fill=State)) +
    geom_col() +
    facet_wrap(~ State)+
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                      decimal.mark = ",", 
                                                      prefix = "", 
                                                      suffix = " €")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    labs(
      title = "Revenue by year and State",
      fill = "State" # Changes the legend name
    )
```







# TASK 2: Data Aquisition
## Part1
To get some data via an API
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(httr)
library(jsonlite)
library(dplyr)
library(tidyverse)
library(rvest)
library(glue)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Wrapped into a function
openlibrary_api_url <- "https://openlibrary.org/dev/docs/api/books"
openlibrary_api <- function(path) {
  url <- modify_url(url = "https://openlibrary.org/dev/docs", path = glue("/api{path}"))
  resp <- GET(url)
  stop_for_status(resp) 
}
resp <- openlibrary_api("/books?bibkeys=ISBN:0451526538")
resp
rawToChar(resp$content)
```


## Part 2- Scraping
Model names and prices for at least one category
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse) 
library(rvest)     
library(jsonlite)  
library(glue)      
library(stringi)
```
COLLECT PRODUCT FAMILIES ---- There was a issue with ,(thousand) and .(decimal) seperations for numbers. So the results were seen as small numbers.
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
  mtb_tbl <- read_html("https://www.rosebikes.de/fahrr%C3%A4der/mtb") %>%
  html_nodes("span.catalog-category-bikes__title-text") %>%
  html_text() %>%
  str_replace_all("\n"," ")
  mtb_tbl
  #as_tibble(mtb_tbl)
  
  mtb_price_tbl <- read_html("https://www.rosebikes.de/fahrr%C3%A4der/mtb") %>%
    html_nodes("div.catalog-category-bikes__price-title") %>%
    html_text() %>%
    str_replace_all("\n"," ")%>%
    
     readr::parse_number()
  mtb_price_tbl
  tibble(mtb_tbl,mtb_price_tbl)
```






  
# TASK 3 - DATA WRANGLING
I have faced many problems with this task. Here is my code.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readr)
```
## Question 1

Reading tables
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#asignee_tbl <- read.delim(
#  file = "assignee.tsv", 
#  sep = "\t",
#)


#patent_asignee_tbl <- read.delim(
 # file = "patent_assignee.tsv", 
#  sep = "\t", 
 # na = c("", "NA", "NULL")
#)
```


Joining table with assignee id
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#asignee_patent_asignee_joined_tbl <- asignee_tbl%>% 
 # left_join( patent_asignee_tbl, by = c( "id"="assignee_id"))
#asignee_patent_asignee_joined_tbl
# arranging ascending order
#asignee_patent_asignee_joined_tbl %>% 
#  filter(type == 2) %>%
#  group_by(organization) %>%
#  filter(!is.na(organization)) %>%
#  filter(!is.na(patent_id)) %>%
#  count(organization,sort =TRUE)
# slice(1:10).I tried slice to get 10 rows but it didn't work. Also I had problem with read and write rds
```

## Question 2
Loading patent table
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#patent_tbl <- read.delim(
 #   file = "patent.tsv", 
#   na = c("", "NA", "NULL")
 # )

# Joining table
#patent_asignee_patent_asignee_joined_tbl <- #asignee_patent_asignee_joined_tbl%>% 
 # left_join( patent_tbl, by = c( "patent_id"="number"))
#asignee_patent_asignee_joined_tbl


#patent_asignee_patent_asignee_joined_tbl%>%
 # filter(type == 2)%>%
  #mutate(year = year(date)) %>%
  #filter(year == 2019) %>%
  #group_by(organization) %>%
  #filter(!is.na(organization)) %>%
  #filter(!is.na(patent_id)) %>%
  #count(organization,sort =TRUE)
#I couldn't check if the code works.It was running for a long time.Sorry my laptop has some issues.
```

## Question 3
Reading table
```{r message=FALSE, warning=FALSE, paged.print=FALSE}

#   file = "uspc.tsv", 
 #   sep = "\t", 
  #  na = c("", "NA", "NULL"),
    #cols_only(patent_id, mainclass_id)
  #)
```
Joining table
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#uspc_patent_asignee_patent_asignee_joined_tbl <- #patent_asignee_patent_asignee_joined_tbl%>% 
 # left_join( uspc_tbl, by = c( "patent_id"="number"))
#asignee_patent_asignee_joined_tbl

#uspc_patent_asignee_patent_asignee_joined_tbl <-        
 # group_by(organization) %>%
  #filter(!is.na(organization)) %>%
  #filter(!is.na(patent_id)) %>%
  #count(organization,sort = TRUE ) %>%
  #count(mainclass_id,sort =TRUE)
```

# TASK 4 - VISUALISATION
I had issues in read_csv. So i couldn't go furthur.
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#library(tidyverse)
#library(ggplot2)
#covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
#covid_data_tbl_4 <- covid_data_tbl 
#  distinct(cases, dateRep, countriesAndTerritories) %>% 
 # filter(countriesAndTerritories == 'Germany' | 
  #         countriesAndTerritories == 'United_Kingdom' | 
   #        countriesAndTerritories == 'Spain' | 
    #       countriesAndTerritories == 'France' | 
     #      countriesAndTerritories == 'United_States_of_America')%>%
 # mutate(date       = lubridate::dmy(dateRep)) %>% 
  #mutate(cumsum = cumsum(cases))
#ggplot(aes(x = dateRep, y = case_sum)) + geom_line()

#labs(title ="Corona cases-World",
 #    x = "year 2020",
#     y = "cumulative cases")
#Question 2
